### 2016-06-19 paper/numerical_experiments.tex
scalar vs field with same fine mesh as other experiments...will try with same reaction coeff as others too...

The error decomposition for three increasing, nested sets of observations and the same QoI region $\Omega_I$ is shown in Figure \ref{fig:dataStudy}. Again, the bottom row gives the baseline case presented in Section~\ref{sec:cdvcdrBaseRef}, although here the basis functions with the largest $5\%$ of the error are choesn, so the proportion of additional refined elements in each iteration is slightly larger. Refinement appears to be consistently most important around the data point closest to $x_1=0$ and the QoI region. However, as more data points are added, it becomes no longer necessarily true that refinement becomes less important around data points as their distance from the QoI region increases. The data points also interact with each other in that placing data points in regions of previously relatively uniform error contribution tends to result in a new error decomposition that is positive or negative around the data points, with valleys of zero magnitude in between.

>>>>

The error decomposition for three increasing, nested sets of observations and the same QoI region $\Omega_I$ is shown in Figure \ref{fig:dataStudy}. Again, the bottom row gives the baseline case presented in Section~\ref{sec:cdvcdrBaseRef}, although here the basis functions with the largest $5\%$ of the error are chosen, so the proportion of additional refined elements in each iteration is slightly larger. Refinement appears to be consistently most important around the data point closest to $x_1=0$ and the QoI region. However, as more data points are added, it becomes no longer necessarily true that refinement becomes less important around data points as their distance from the QoI region increases. The data points also interact with each other in that placing data points in regions of previously relatively uniform error contribution tends to result in a new error decomposition that is positive or negative around the data points, with valleys of zero magnitude in between.
